---
title: "PH142 Fall 2022 Final Exam"
subtitle: "Working Rmd for final"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options: 
  chunk_output_type: console
---

```{r, include = F}

library(tidyverse)
library(broom)
library(dplyr)
library(ggplot2)
library(tibble)
```

The exam is open note. This means you can use electronic or hard copies of all class materials and datahub if you wish.\

While you take the exam, please do not collaborate on the test with anyone.\

Below, we share some commands for reading in data and load libraries you might use.   You can either do your calculations by hand (if possible) or use R functions.  Thus, when just a table is available (not a data file already made) you can use R to create a data.frame (or tibble) and use R functions to calculate the quantities requested.  You are under no obligation to use this file or datahub, but you will need to use RStudio.

Make sure you are ready to go, with all the materials available, when you begin the exam.  You 


\newpage

## Question 12 


```{r, echo = T, eval=T}
dating <- read_csv("dating_data.csv")
head(dating)
```

## Question 13 


```{r, echo=T}
load("Ques23.rdata")
```


## Question 14 


```{r, include = T, eval=T}
cereal <- read_csv("UScereal.csv")
```

