---
title: 'Lab07: Plots of the sampled means and their confidence intervals'
output: pdf_document
---

This file is for the GSI, though you can run the code too if you'd like.

The following chunk installs googlesheets4, a predecessor of the googlesheets package.
```{r}
install.packages("googlesheets4")
```

```{r import-gs4-key}
library(googlesheets4)
library(dplyr)
library(ggplot2)
# fyi, sheet URLs (you might not need these, but make sure you first open the sheet in your browser or the following code won't run.)

# Lab 101B: https://docs.google.com/spreadsheets/d/1LP7HRfcQwGP4LGYqTwoaD-ei3nJACZjhxvHwQr36S7A/edit#gid=0
# Lab 102B: https://docs.google.com/spreadsheets/d/1lCuMM6fpiaevljkOaDqxMzZfFqlbqjRfBeuz9BnXfBA/edit#gid=0
# Lab 103B: https://docs.google.com/spreadsheets/d/1TlQ1Ho72w1PbFZgjBvUMW1TPHoWKj1dMi_wVlHY_C2M/edit#gid=0
# Lab 104B: https://docs.google.com/spreadsheets/d/1oErxTGfg4eKz_quMlaU1cMZGaZdUabrYVJpGTpIoy_o/edit#gid=0
# Lab 105B: https://docs.google.com/spreadsheets/d/1WB8ofYnnjsbRPmbkoHkt5PHELJsZuR1ug-RK5v_Ra_Q/edit#gid=0
# Lab 106B: https://docs.google.com/spreadsheets/d/1x1ayTKVeKFw26Wz0UzNqDLTqOc1bVi5Riz5ib0Ej3Gg/edit#gid=0
# Lab 107B: https://docs.google.com/spreadsheets/d/1adtnUq-Xajf65ieD9gcfo7ZBNyytwSGHdXm1FyAarYU/edit#gid=0
# Lab 108B: https://docs.google.com/spreadsheets/d/1e7oWNLTnQSy_zYHMwnKS8wkpBZVOmc_0JYmVboKICY4/edit#gid=0
# Lab 109B: https://docs.google.com/spreadsheets/d/1J7wmPe52QIDEbXeojyHOiv9HGKOzruA3yQJaP0Mee4U/edit#gid=0
# Lab 110B: https://docs.google.com/spreadsheets/d/1hAQW2hlcnbH0fW-Dpk6OQ8j-THCYe8k5im-rBbeLSVU/edit#gid=0
# Lab 111B: https://docs.google.com/spreadsheets/d/1Lab1EfkHZ4z6TI7BfJz3TiIHx7yf8fbz0UwuD99Fkbc/edit#gid=0


# Uncomment your my_key object for your lab 

#Lab 101B: my_key <- "1LP7HRfcQwGP4LGYqTwoaD-ei3nJACZjhxvHwQr36S7A"
#Lab 102B: my_key <- "1lCuMM6fpiaevljkOaDqxMzZfFqlbqjRfBeuz9BnXfBA"
#Lab 103B: my_key <- "1TlQ1Ho72w1PbFZgjBvUMW1TPHoWKj1dMi_wVlHY_C2M"
#Lab 104B: my_key <- "1oErxTGfg4eKz_quMlaU1cMZGaZdUabrYVJpGTpIoy_o"
#Lab 105B: my_key <- "1WB8ofYnnjsbRPmbkoHkt5PHELJsZuR1ug-RK5v_Ra_Q"
#Lab 106B: my_key <- "1x1ayTKVeKFw26Wz0UzNqDLTqOc1bVi5Riz5ib0Ej3Gg"
#Lab 107B: my_key <- "1adtnUq-Xajf65ieD9gcfo7ZBNyytwSGHdXm1FyAarYU"
#Lab 108B: my_key <- "1e7oWNLTnQSy_zYHMwnKS8wkpBZVOmc_0JYmVboKICY4"
#Lab 109B: my_key <- "1J7wmPe52QIDEbXeojyHOiv9HGKOzruA3yQJaP0Mee4U"
#Lab 110B: my_key <- "1hAQW2hlcnbH0fW-Dpk6OQ8j-THCYe8k5im-rBbeLSVU"
#Lab 111B: my_key <- "1Lab1EfkHZ4z6TI7BfJz3TiIHx7yf8fbz0UwuD99Fkbc"
```

Run the chunk below to authenticate your berkeley.edu account with the Tidyverse API Package.

*Make sure you click on the third checkbox to allow Tidyverse to read your sheets.*
- If you didn't check the box, you will receive the following error: `Client error: (403) Permission Denied`
- To resolve the error above, just rerun the chunk below and make sure you select the third checkbox option.
- You should be able to import data from your google sheets once permission is given.

```{r gs-auth}
gs4_auth(
  scopes = 'https://www.googleapis.com/auth/spreadsheets',
  path = Sys.getenv('GOOGLE_DRIVE_KEY')
)
```

If the line segments are too smushed, change the range of the google sheets to fit close to the total number of observations on the google sheet (e.g. if there are a total of ~50 observations from all of your students combined, set the range from A1 to F55).

```{r sample-size-10}
our_sheet_ss_10 <- read_sheet(my_key, range = "A1:F300")

our_sheet_ss_10 <- our_sheet_ss_10 %>% 
  mutate(missed = ((lower_CI > 70) & (upper_CI > 70)) | ((lower_CI < 70) & (upper_CI < 70)))
CI_plot_n10 <- ggplot(our_sheet_ss_10, aes(x = sample_mean_heights, y = sample_id)) +
  geom_point(aes(col = missed)) +
  geom_point() + 
  geom_segment(aes(x = lower_CI, xend = upper_CI, yend = sample_id, col = missed)) +
  geom_vline(xintercept = 70, col = "blue") +
  labs(y = "Sample", x = "Sample mean", title = "95% CIs, when sample size = 10") + 
  scale_x_continuous(limits = c(65, 75)) + 
  scale_y_continuous(limits = c(0, 20))
CI_plot_n10
```


```{r sample-size-50}
our_sheet_ss_50 <- read_sheet(my_key, sheet = "n = 50", range = "A1:F300")

#our_sheet_ss_50 <- shared_gs %>% gs_read("n = 50")
our_sheet_ss_50 <- our_sheet_ss_50 %>% 
  mutate(missed = ((lower_CI > 70) & (upper_CI > 70)) | ((lower_CI < 70) & (upper_CI < 70)))
CI_plot_n50 <- ggplot(our_sheet_ss_50, aes(x = sample_mean_heights, y = sample_id)) +
  geom_point() + 
  geom_segment(aes(x = lower_CI, xend = upper_CI, yend = sample_id)) +
  geom_vline(xintercept = 70, col = "blue") +
  labs(y = "Sample", x = "Sample mean", title = "95% CIs, when sample size = 50") + 
  scale_x_continuous(limits = c(65, 75)) + 
  scale_y_continuous(limits = c(0, 50))
CI_plot_n50
```

```{r samples-size-500}
our_sheet_ss_500 <- read_sheet(my_key, sheet = "n = 500", range = "A1:F300")

our_sheet_ss_500 <- our_sheet_ss_500 %>% 
  mutate(missed = ((lower_CI > 70) & (upper_CI > 70)) | ((lower_CI < 70) & (upper_CI < 70)))
CI_plot_n500 <- ggplot(our_sheet_ss_500, aes(x = sample_mean_heights, y = sample_id)) +
  geom_point() + 
  geom_segment(aes(x = lower_CI, xend = upper_CI, yend = sample_id)) +
  geom_vline(xintercept = 70, col = "blue") +
  labs(y = "Sample", x = "Sample mean", title = "95% CIs, when sample size = 500") + 
  scale_x_continuous(limits = c(65, 75))
CI_plot_n500
```

Run this code if you want to simulate on your own many samples:

```{r}
alameda_pop <- read.csv("data/L07_Alameda.csv")
known_pop_sd <- 2.786314


sample_size <- 10 
calc_sample_stats <- function(df) {
  df %>% 
    summarize(mean_heights = mean(height)) %>%
    mutate(lower_CI = mean_heights - 1.96 * known_pop_sd / sqrt(sample_size),
           upper_CI = mean_heights + 1.96 * known_pop_sd / sqrt(sample_size))
  
}
many.sample.stats <- replicate(1000, sample_n(alameda_pop, sample_size), simplify = F) %>%
  lapply(., calc_sample_stats) %>%
  bind_rows() %>%
  mutate(sample.id = 1:n())
many.sample.stats <- many.sample.stats %>% mutate(missed = ((lower_CI > 70) & (upper_CI > 70)) | 
                                                    ((lower_CI < 70) & (upper_CI < 70)))
ggplot(many.sample.stats %>% filter(sample.id < 100), aes(x = mean_heights, y = sample.id)) + 
  geom_point(aes(col = missed)) + 
  geom_segment(aes(x = lower_CI, xend = upper_CI, yend = sample.id, col = missed)) +
  geom_vline(xintercept = 70, col = "blue") +
  labs(y = "Sample", x = "Sample mean", title = paste0("95% CIs, when sample size = ", sample_size)) + 
  scale_x_continuous(limits = c(65, 75))
```

